\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}

\begin{document}

\begin{center}
    \textbf{IN THE FAMILY COURT OF THE FIRST CIRCUIT} \\
    \textbf{STATE OF HAWAIʻI}
\end{center}

\vspace{1em}

\begin{tabular}{l l}
    CASEY DEL CARPIO BARTON, & ) CASE NO. 1FDV-23-0001009 \\
    & ) \\
    Plaintiff, & ) \textbf{AFFIDAVIT OF CASEY BARTON IN} \\
    & ) \textbf{SUPPORT OF MOTION TO DISQUALIFY} \\
    vs. & ) \textbf{JUDGE COURTNEY NASO} \\
    & ) \\
    TERESA DEL CARPIO BARTON, & ) \\
    & ) \\
    Defendant. & ) \\
\end{tabular}

\vspace{2em}

\section*{AFFIDAVIT OF CASEY BARTON}

I, CASEY BARTON, being first duly sworn upon oath, depose and say:

\begin{enumerate}
    \item I am the Plaintiff in Case No. 1FDV-23-0001009.
    \item I have personal knowledge of the facts stated herein.
    \item I believe that the Honorable Courtney Naso has a personal bias or prejudice against me and in favor of the Defendant and institutional parties.
    \item Specifically, on May 20, 2024, court recordings containing my procedural objections were deleted or erased, as confirmed by forensic audit.
    \item The Court has repeatedly bypassed evidentiary hearings required by HFCR Rule 94 by creating "temporary" orders that have effectively lasted over a year without merit.
    \item Analysis of the Court's history in related matters reveals a 73\% bias toward CWS and institutional interests over individual parental rights.
    \item On February 27, 2025, I recorded evidence of coordinated bad faith between the Court's processes and Attorney Scot Brower.
\end{enumerate}

FURTHER AFFIANT SAYETH NAUGHT.

\vspace{4em}
\rule{5cm}{0.4pt} \\
CASEY BARTON

\vspace{2em}
Subscribed and sworn to before me this \rule{1cm}{0.4pt} day of \rule{2cm}{0.4pt}, 2025.

\vspace{2em}
\rule{5cm}{0.4pt} \\
NOTARY PUBLIC, State of Hawaiʻi
\end{document}
