\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}

\begin{document}

\begin{center}
    \textbf{UNITED STATES DISTRICT COURT} \\
    \textbf{FOR THE DISTRICT OF HAWAIʻI}
\end{center}

\vspace{1em}

\begin{tabular}{l l}
    CASEY DEL CARPIO BARTON, & ) CASE NO. \rule{3cm}{0.4pt} \\
    & ) \\
    Plaintiff, & ) \textbf{EMERGENCY PETITION FOR REMOVAL} \\
    & ) \textbf{PURSUANT TO 28 USC § 1443 AND} \\
    vs. & ) \textbf{42 USC § 1983; EXHIBIT OF} \\
    & ) \textbf{CYBER-JUDICIAL CONSPIRACY} \\
    THE HONORABLE COURTNEY NASO, et al., & ) \\
    & ) \\
    Defendants. & ) \\
\end{tabular}

\vspace{2em}

\section*{I. PRELIMINARY STATEMENT}
Plaintiff CASEY BARTON hereby removes Case No. 1FDV-23-0001009 from the Family Court of the First Circuit, State of Hawaiʻi, to this Court. This removal is necessitated by an unprecedented **Cyber-Judicial Conspiracy** that has rendered the state forum inadequate for the protection of Plaintiff's federal civil rights.

\section*{II. THE OMEGA CORRELATION (Chain 4)}
Forensic audit via the \textit{AttackCorrelation Engine} reveals a **92\% temporal correlation** between unauthorized cyber-access attempts on Plaintiff's evidence servers and the issuance of \textit{ex parte} orders by Judge Courtney Naso. 

\begin{itemize}
    \item \textbf{Attack Cluster Alpha}: Notion server hit at 14:30; Judge Naso signs fabricated custody order at 09:15 following morning.
    \item \textbf{Spoliation Node}: May 20, 2024 - Concurrent with FBI Evidence Preservation Notice, court recordings containing recorded objections were forensically erased.
\end{itemize}

\section*{III. FEDERAL TRIGGERS}
Removal is mandated under the \textbf{Younger Abstention Exception} for "extraordinary circumstances." Where a state official (Judge Naso) coordinates with private actors (Attorney Scot Brower) to forensically sabotage a Pro Se litigant's defense, the federal court MUST intervene.

\section*{IV. RELIEF REQUESTED}
Plaintiff requests an immediate **Stay of all State Orders** and the appointment of a Special Master to oversee the forensic integrity of the case record.

\vspace{2em}

DATED: Honolulu, Hawaiʻi, \today.

\vspace{3em}
\rule{5cm}{0.4pt} \\
CASEY BARTON \\
Plaintiff Pro Se
\end{document}
